\textbf{EECS 340: Assignment 6}

### 2020-04-20 assignment_6/article.tex
✨ Add Problem 1 responses.
✨ Add Problem 3(a) response.

@@

@@

@@

@@

>>>>

Hi Grader! Please note the boxes in following diagrams are merely provided for visualization purposes, they are not propertionaly graphed. Thanks.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\linewidth]{{fig/fig_1_a.png}}
    \label{fig:1_a}
\end{figure}

\begin{itemize}
    \item Greedy Choice: \ilc{(a1)}
    \item Optimal Choice: \ilc{(a2, a3)}
\end{itemize}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\linewidth]{{fig/fig_1_b.png}}
    \label{fig:1_a}
\end{figure}

\begin{itemize}
    \item Greedy Choice: \ilc{(a1)}
    \item Optimal Choice: \ilc{(a2, a3)}
\end{itemize}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\linewidth]{{fig/fig_1_c.png}}
    \label{fig:1_a}
\end{figure}

\begin{itemize}
    \item Greedy Choice: \ilc{(a1)}
    \item Optimal Choice: Any combination between one of \ilc{\{a2, a4, a5, a6\}} and one of \ilc{\{a3, a7, a8, a9\}}.
\end{itemize}

@@

Assume we have a set of coins with value of $\{\$1, \$5, \$8\}$ and we are looking to exchange $n = 20$.\newline

The greedy chioce will lead to a solution $\{2 \times \$8, 4 \times \$1\}$ for a totle of $6$ coins, however the optimal solution should be $\{4 \times \$5\}$ for total of $4$ coins. $4 < 6$ and thus disprove the greedy choice property.
